---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  include = TRUE,
  echo = TRUE
)
```

# voicer

Chord voicing is the art of assigning pitch heights to pitch classes.
This package, `voicer`, 
optimises the voicings of chord sequences according to an objective cost function.
The Viterbi algorithm is used to guarantee solution optimality.

Status: **pre-alpha**

## Example usage

`voice` is the main function to use.
We pass `voice` vectors of chords as created by the `hrep` package.
Important chord representations from the `hrep` package are:

- `pc_set()` - create a pitch-class set (unordered pitch classes from 0 to 11)
- `pc_chord()` - create a pitch-class chord
(a pitch-class set where the bass note is identified)
- `pi_chord()` - create a pitch chord (pitches as MIDI note numbers)

```{r}
library(hrep)
library(magrittr)
library(voicer)

pc_set(c(0, 4, 7))
pc_chord(4, c(0, 4, 7))
pi_chord(c(60, 64, 67))
```

Using the function `vec` from the `hrep` package, 
we combine lists of chords into typed vectors.

```{r}
x <- list(pc_set(c(0, 4, 7)), 
          pc_set(c(0, 5, 9)),
          pc_set(c(2, 7, 11)), 
          pc_set(c(0, 4, 7))) %>% vec("pc_set")
x
```

We can then pass the resulting object to `voice`.

```{r}
y <- voice(x)
y 
as.list(y)
```

We can do the same for vectors of type `pc_chord` and `pi_chord`.

```{r}
list(pc_chord(0, c(4, 7)), 
     pc_chord(9, c(0, 5)),
     pc_chord(7, c(2, 11)), 
     pc_chord(0, c(4, 7))) %>% 
  vec("pc_chord") %>% 
  voice() %>% 
  as.list()
```

By default, revoicing chords of type `pi_chord` preserves
the pitch-class of the bass note.
To allow different inversions,
you can first convert your `pi_chord` objects to `pc_set` objects.

```{r}
list(pi_chord(c(60, 64, 67)), 
     pi_chord(c(60, 65, 69)),
     pi_chord(c(62, 67, 71)), 
     pi_chord(c(60, 64, 67))) %>% 
  vec("pi_chord") %>% 
  voice() %>% 
  as.list()
```

By default, revoicing chords of type `pi_chord` also preserves
the number of occurrences of each pitch class in the chord.
This, and other behaviours,
can be changed using the `opt` argument to `voice()`.
