---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  include = TRUE,
  echo = TRUE,
  cache = TRUE
)
```

# voicer

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/pmcharrison/voicer.svg?branch=master)](https://travis-ci.org/pmcharrison/voicer)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/pmcharrison/voicer?branch=master&svg=true)](https://ci.appveyor.com/project/pmcharrison/voicer)
[![Coverage status](https://coveralls.io/repos/github/pmcharrison/voicer/badge.svg)](https://coveralls.io/r/pmcharrison/voicer?branch=master)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2613565.svg)](https://doi.org/10.5281/zenodo.2613565)


Chord voicing is the art of assigning pitch heights to pitch classes.
This package, `voicer`, 
optimises the voicings of chord sequences according to an objective cost function.
The Viterbi algorithm is used to guarantee solution optimality.

## Paper

Harrison, P. M. C., & Pearce, M. T. (2019). 
A computational model for the analysis and generation of chord voicings.
*PsyArXiv*. 
[doi:10.31234/osf.io/wrgj7](https://doi.org/10.31234/osf.io/wrgj7)

## Example usage

`voice` is the main function to use.
We pass `voice` vectors of chords as created by the `hrep` package.
Important chord representations from the `hrep` package are:

- `pc_set()` - create a pitch-class set (unordered pitch classes from 0 to 11)
- `pc_chord()` - create a pitch-class chord
(a pitch-class set where the bass note is identified)
- `pi_chord()` - create a pitch chord (pitches as MIDI note numbers)

```{r}
library(hrep)
library(magrittr)
library(voicer)

pc_set(c(0, 4, 7))
pc_chord(c(4, 0, 7))
pi_chord(c(60, 64, 67))
```

Using the function `vec` from the `hrep` package, 
we combine lists of chords into typed vectors.

```{r}
x <- list(pc_set(c(0, 4, 7)), 
          pc_set(c(0, 5, 9)),
          pc_set(c(2, 7, 11)), 
          pc_set(c(0, 4, 7))) %>% vec("pc_set")
x
```

We can then pass the resulting object to `voice`.

```{r}
y <- voice(x)
y 
as.list(y)
```

We can do the same for vectors of type `pc_chord`.

```{r}
list(pc_chord(c(0, 4, 7)), 
     pc_chord(c(9, 0, 5)),
     pc_chord(c(7, 2, 11)), 
     pc_chord(c(0, 4, 7))) %>% 
  vec("pc_chord") %>% 
  voice() %>% 
  as.list()
```

See `?voice` for more details.
